\thetitle

### 2020-11-22 sun_phases/spin_qudit_tomo.tex
comment on the wigner function tomography work in schmied2011tomographic

The problem of qudit tomography in particular is not new, with an extensive literature on a variety of techniques \cite{manko1997spin, thew2002qudit, flammia2005minimal, salazar2012quantum, sosa-martinez2017quantum, ha2018minimal, evrard2019enhanced, stefano2019set, palici2020oam}.
However, existing protocols either require the capability to perform essentially arbitrary operations on a qudit \cite{thew2002qudit, flammia2005minimal, salazar2012quantum, sosa-martinez2017quantum, ha2018minimal, stefano2019set, palici2020oam}, or rely on infinite-dimensional representations of a quantum spin \cite{manko1997spin, evrard2019enhanced}, resulting in tomographic protocols that can be highly inefficient or unachievable in practice.
The protocols based on infinite-dimensional representations of a quantum spin have the advantage of reconstructing its state from measurements of spin projection onto different spatial axes, which are generally accessible with any spin qudit.
Nonetheless, these protocols obfuscate the actual requirements for performing full state tomography, provide no straightforward error bounds or guarantees of accuracy, and extract only a small faction of the information contained in measurement data.

>>>>

The problem of qudit tomography in particular is not new, with an extensive literature on a variety of techniques \cite{manko1997spin, schmied2011tomographic, evrard2019enhanced, flammia2005minimal, thew2002qudit, salazar2012quantum, sosa-martinez2017quantum, ha2018minimal, stefano2019set, palici2020oam}.
However, existing protocols either rely infinite-dimensional representations of a quantum spin \cite{manko1997spin, schmied2011tomographic, evrard2019enhanced}, or require the capability to perform essentially arbitrary operations on a qudit \cite{thew2002qudit, flammia2005minimal, salazar2012quantum, sosa-martinez2017quantum, ha2018minimal, stefano2019set, palici2020oam}, resulting in tomographic protocols that can be highly inefficient or unachievable in practice.
The protocols based on infinite-dimensional representations of a quantum spin have the advantage of reconstructing its state from measurements of spin projection onto different spatial axes, which are generally accessible with any spin qudit.
Nonetheless, these protocols obfuscate the actual requirements for performing full state tomography, provide no straightforward error bounds or guarantees of accuracy, and (with the exception of Ref.~\cite{schmied2011tomographic}) extract only a small faction of the information contained in measurement data.
